Impact of Training Variability on Visuomotor Function Learning and Extrapolation

### 2024-05-21 Sections/htw_full.qmd
fix headings

---
title: Impact of Training Variability on Visuomotor Function Learning and Extrapolation
author:
- name: Thomas E. Gorman
  affiliations: 
   - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Robert L. Goldstone
  affiliation: Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://pc.cogs.indiana.edu/
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
repo-actions: false
execute: 
  warning: false
  eval: true
format:
  html: 
    date: last-modified
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: htw_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: htw_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "htw.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "htw.docx"
    toc: true
prefer-html: true
---

@@

## Experiment 1

### Methods

@@

### Analyses Strategy

@@

### Results

@@

## E1 Summary

@@

## Experiment 2

@@

### Methods & Procedure

@@

### Experiment 2 Summary

@@

## Experiment 3

@@

### Experiment 3 Summary

@@

## Computational Model

@@

### ALM & Exam

@@

### Model Fitting

@@

### Modelling Results

>>>>

---
title: Impact of Training Variability on Visuomotor Function Learning and Extrapolation
author:
- name: Thomas E. Gorman
  affiliations: 
   - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Robert L. Goldstone
  affiliation: Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://pc.cogs.indiana.edu/
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
repo-actions: false
execute: 
  warning: false
  eval: true
format:
  html: 
    date: last-modified
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: htw_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: htw_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "htw.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "htw.docx"
    toc: true
prefer-html: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
---

@@

# Experiment 1

## Methods

@@

## Analyses Strategy

@@

## Results

@@

## Experiment 1 Summary

@@

# Experiment 2

@@

## Methods & Procedure

@@

## Experiment 2 Summary

@@

# Experiment 3

@@

## Experiment 3 Summary

@@

# Computational Model

@@

## ALM & Exam

@@

## Model Fitting

@@

## Modelling Results
